\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-05-01 paper.tex
Tikzified HATP plans

@@

The planner also generates synchronisation points between the agents.
Figure~\ref{plan_hatp1} illustrates such a plan with two streams.  Here, the
robot needs to wait for the success of the human agent's {\tt THROW} action
(estimated through the fulfilment of the action post-conditions, typically
$\neg$\stmt{GREY\_TAPE isOn TABLE}) to be able to start its own action.

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\columnwidth]{first_plan.pdf}
  \caption{A plan produced by HATP with 2 streams}
  \label{plan_hatp1}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\columnwidth]{second_plan.pdf}
  \caption{A plan with the wasted time social rule. {\tt PUTRV} stands for {\it Put it so it is both Reachable and Visible}.}
  \label{plan_hatp2}
\end{figure}

@@

\begin{figure*}[thpb]
  \centering
  \includegraphics[width=1.0\textwidth]{third_plan.pdf} \\
  \caption {A plan produced by HATP to execute the high-level order ``clean the table''. Two streams of actions are generated: for the human (top) and for the robot(bottom). Synchronization points ensure the coordination.}
  \label{plan-etat2}
\end{figure*}

>>>>

\newcommand{\action}[3]{#1\\\textsf{\scriptsize #2,}\\\textsf{\scriptsize #3}}

@@

The planner also generates synchronisation points between the agents.
Figure~\ref{plan_hatp1} illustrates such a plan with two streams.  Here, the
robot needs to wait for the success of the human agent's {\tt PUT} action
(estimated through the fulfilment of the action post-conditions, typically
$\neg$\stmt{GREY\_TAPE isOn TABLE}) to be able to start its own action.

@@

\begin{figure}[htbp]
    \centering
\resizebox{0.9\textwidth}{!}{%
\begin{tikzpicture}[
    >=latex,
    robot/.style={fill=RoyalBlue!50},
    every edge/.style={<-, draw, ultra thick},
    every node/.style={ draw, 
                        thick,  
                        circle, 
                        font=\sf,
                        align=center,
                        node distance=2cm,
                        fill=BurntOrange!50, 
                        minimum size=2cm, 
                        inner sep=0.1cm}]

    \node (h1) {TAKE\\{\tiny \it \sf GREY\_TAPE, TABLE}};
    \node[right=of h1] (h2) {PUT\\{\tiny\it\sf GREY\_TAPE, BIN1 }} edge (h1);

    \node[robot, below=1.5 of h1] (r1) {TAKE\\{\tiny \it \sf BLACK\_TAPE, TABLE }};
    \node[robot, right=of r1] (r2) {PUT\\{\tiny \it \sf BLACK\_TAPE, BIN2 }} edge (r1);
    \node[robot, right=of r2] (r3) {TAKE\\{\tiny \it \sf BOTTLE, TABLE }} edge (r2);
    \node[robot, right=of r3] (r4) {PUTRV\\{\tiny \it \sf BOTTLE, TABLE}} edge (r3);
    \node[robot, right=of r4] (r5) {TAKE\\{\tiny \it \sf BOOK, TABLE }} edge (r4);
    \node[robot, right=of r5] (r6) {PUT\\{\tiny \it \sf BOOK, BIN2 }} edge (r5);

    \node[right=9cm of h2] (h3) {TAKE\\{\tiny \it \sf BOTTLE, TABLE}} edge (h2) edge (r4);
    \node[right=of h3] (h4) {PUT\\{\tiny \it \sf BOTTLE, BIN1}} edge (h3);

\end{tikzpicture}
}
\caption{A plan produced by HATP with two action streams (here, human actions
    are at the top while robot actions are at the bottom). The arrow between the
    two streams represents a synchronization point ({\sf PUTRV} stands for {\it Put it so it is both
    reachable and visible}).}

  \label{plan_hatp1}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
\resizebox{0.9\textwidth}{!}{%
\begin{tikzpicture}[
    >=latex,
    robot/.style={fill=RoyalBlue!50},
    every edge/.style={<-, draw, ultra thick},
    every node/.style={ draw, 
                        thick,  
                        circle, 
                        font=\sf,
                        align=center,
                        node distance=2cm,
                        fill=BurntOrange!50, 
                        minimum size=2cm, 
                        inner sep=0.1cm}]

    \node (h1) {TAKE\\{\tiny \it \sf GREY\_TAPE, TABLE}};
    \node[right=of h1] (h2) {PUT\\{\tiny\it\sf GREY\_TAPE, BIN1 }} edge (h1);

    \node[robot, below=1.5 of h1] (r3) {TAKE\\{\tiny \it \sf BOTTLE, TABLE }};
    \node[robot, right=of r3] (r4) {PUTRV\\{\tiny \it \sf BOTTLE, TABLE}} edge (r3);
    \node[robot, right=of r4] (r1) {TAKE\\{\tiny \it \sf BLACK\_TAPE, TABLE }} edge (r4);
    \node[robot, right=of r1] (r2) {PUT\\{\tiny \it \sf BLACK\_TAPE, BIN2 }} edge (r1);
    \node[robot, right=of r2] (r5) {TAKE\\{\tiny \it \sf BOOK, TABLE }} edge (r2);
    \node[robot, right=of r5] (r6) {PUT\\{\tiny \it \sf BOOK, BIN2 }} edge (r5);

    \node[right=of h2] (h3) {TAKE\\{\tiny \it \sf BOTTLE, TABLE}} edge (h2) edge (r4);
    \node[right=of h3] (h4) {PUT\\{\tiny \it \sf BOTTLE, BIN1}} edge (h3);

\caption{An alternative plan where the \emph{wasted time} social rule is used to optimize the
total duration of the task. }

  \label{plan_hatp2}
\end{figure}

@@

\begin{figure*}[thpb]
  \centering
\resizebox{0.9\textwidth}{!}{%
\begin{tikzpicture}[
    >=latex,
    robot/.style={fill=RoyalBlue!50},
    every edge/.style={<-, draw, ultra thick},
    every node/.style={ draw, 
                        thick,  
                        circle, 
                        font=\sf,
                        align=center,
                        node distance=2cm,
                        fill=BurntOrange!50, 
                        minimum size=2cm, 
                        inner sep=0.1cm}]

    \node (h1) {\action{TAKE}{WALLE\_TAPE}{TABLE}};
    \node[right=of h1] (h2) {\action{THROW}{WALLE\_TAPE}{TRASH\_1 }} edge (h1);

    \node[robot, below=1.5 of h1] (r1) {\action{TAKE}{GREY\_TAPE}{TABLE }};
    \node[robot, right=of r1] (r2) {\action{PUTRV}{GREY\_TAPE}{TABLE}} edge (r1);
    \node[robot, right=of r2] (r3) {\action{TAKE}{LOTR\_TAPE}{TABLE }} edge (r2);
    \node[robot, right=of r3] (r4) {\action{PUTRV}{LOTR\_TAPE}{TABLE }} edge (r3);

    \node[right=of h2] (h3) {\action{TAKE}{GREY\_TAPE}{TABLE}} edge (h2) edge (r2);
    \node[right=of h3] (h4) {\action{THROW}{GREY\_TAPE}{TRASH\_1}} edge (h3);
    \node[right=of h4] (h5) {\action{TAKE}{LOTR\_TAPE}{TABLE}} edge (h4) edge (r4);
    \node[right=of h5] (h6) {\action{THROW}{LOTR\_TAPE}{TRASH\_1}} edge (h5);

  \caption {A plan produced by HATP to execute the high-level order ``clean the
  table''. Two streams of actions are generated: for the human (top) and for the
  robot (bottom). Synchronization points ensure the coordination.}

  \label{plan-etat2}
\end{figure*}
